---
title: "Terlipressin vs. Off-Label Vasoconstrictors in HRS-AKI"
subtitle: "Matched-cohort analysis of treatment response and 90-day outcomes"
date: today
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-location: left
    toc-title: "Contents"
    toc-expand: 2
    number-sections: true
    number-depth: 3
    code-fold: true
    code-summary: "Show code"
    code-tools: true
    code-overflow: wrap
    fig-width: 7
    fig-height: 5
    fig-align: center
    tbl-cap-location: top
    anchor-sections: true
    smooth-scroll: true
    include-in-header:
      text: |
        <style>
          .quarto-title-block .quarto-title-banner { background: #2c8dbb; }
          h2 { border-bottom: 2px solid #e3e8ee; padding-bottom: .3rem; margin-top: 2.2rem; }
          h3 { margin-top: 1.6rem; color: #23527c; }
          #quarto-margin-sidebar, #TOC { font-size: .9rem; }
          .gt_table { font-size: 13.5px; }
          table.table { font-size: 13.5px; }
          .cell-output-display { margin-bottom: 1.1rem; }
        </style>
execute:
  warning: false
  message: false
---

# Overview {#sec-overview}

This report compares patients with hepatorenal syndrome–acute kidney injury (HRS-AKI)
treated with **terlipressin** against a historical cohort treated with **off-label
vasoconstrictors** (midodrine/octreotide, norepinephrine, or vasopressin).

| Item | Definition |
|:-----|:-----------|
| Terlipressin cohort | HARMONY multi-center registry (`group = "terli"`) |
| Off-label cohort | Prior multi-center HRS registry, restricted to `final_type_of_aki == 2` and `hrs_vasoconstrictor == 1` (`group = "hrs"`) |
| Treatment response | `hrs_responders_cat_2`: **1** = complete or partial response, **0** = no response |
| Follow-up time | `time_90days` — days from treatment initiation, truncated at 90 |
| 90-day status | `status_90days` — **0** = alive/censored, **1** = death, **2** = liver transplant (competing event) |
| Matching | 1:1 nearest-neighbour propensity score, caliper 0.2 SD |

::: {.callout-note}
## How to read this report
All code is folded by default — use **Show code** on any block, or the `</> Code`
menu at the top right to expand everything. Sections **5** and **6** contain the
creatinine–response tables and the new 90-day survival analyses.
:::

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(tableone)
library(writexl)
library(gtsummary)
library(survival)
library(ggplot2)
library(readxl)
library(ggpubr)
library(splines)
library(xlsx)
library(lattice)
library(mice)
library(DescTools)
library(survminer)
library(finalfit)
library(tidycmprsk)
library(ggsurvfit)
library(sqldf)
library(table1)
library(cobalt)
library(MatchIt)
library(gt)
library(knitr)
library(kableExtra)

# En dashes and >= symbols in table labels only survive a UTF-8 locale; a bare
# `quarto render` from a shell without LANG set otherwise escapes them as <U+2013>.
if (!isTRUE(l10n_info()$`UTF-8`)) {
  try(Sys.setlocale("LC_CTYPE", "en_US.UTF-8"), silent = TRUE)
}

# Shared colours used throughout the report
col_no_resp <- "#c0392b"
col_resp    <- "#2c8dbb"
col_hrs     <- "#e08214"
col_terli   <- "#2c8dbb"
```

# Data preparation {#sec-data}

## Terlipressin cohort (HARMONY)

Variables are coerced to numeric where possible, renamed to a common schema shared
with the off-label cohort, and re-coded so that categorical levels line up across
the two registries.

```{r}
#| label: prep-terli

terlipressin <- read_xlsx("/Users/to909/Desktop/Terlipressin/final_master_0508.xlsx")

terlipressin_numeric <- terlipressin  # make a copy

for (col in names(terlipressin_numeric)) {
  # Suppress warnings like "NAs introduced by coercion"
  converted <- suppressWarnings(as.numeric(terlipressin_numeric[[col]]))

  # If at least one value successfully converted (not NA), keep it
  if (any(!is.na(converted))) {
    terlipressin_numeric[[col]] <- converted
  }
}

terlipressin_numeric <- terlipressin_numeric %>%
  mutate(
    group = "terli",
    death_discharge = ifelse(disposition == 5, 1, 0)
  ) %>%
  rename(
    terli_resfailuretype_day2 = terli_resfailuretype_day1_day2
  ) %>%
  select(-any_of(c("fena"))) %>%
  rename(
    age_admission = age,
    sex = sex_male,
    White = race,
    hispanic_race = hispanic,
    loop_diuretic = diuretics_preadmission,
    aldosterone_antagonist = potsp_diuretic_preadmission,
    lactulose = lactulose_preadmission,
    rifaximin = rifaximin_preadmission,
    prophylactic_antibiotic = sbp_ppx_preadmission,
    nsaids = nsaid_preadmission,
    beta_blockers = nsbb_preadmission,
    albumin_amount_admission = totalalbumin_before_terli, # changed 1129
    diabetes = dm_medical_hx,
    cad = cad_medical_hx,
    htn = htn_medical_hx,
    etiology_cirrhosis = cirrhosis_etiology,
    ascites_admission = ascites_previous_comp,
    encephalopathy_admission = he_previous_comp,
    gi_bleed_admission = gibleed_hosp,
    peritonitis_admission = sbp_previous_comp,
    hcc_admission = hcc_previous_comp,
    tips_admission = tips_previous_comp,
    na_admit = na_terli_day0,
    k_admit = k_terli_day0,
    cl_admit = chloride_terli_day0,
    co2_admit = bicarb_terli_day0,
    bun_admit = bun_terli_day0,
    urine_creatinine = ua_cr_value_hrs,
    fena = fena_hrs,
    he_grade_admission = hegrade_admit,
    baseline_creatinine = baseline_scr,
    CLIF_C_Score = clif_c_score,
    aclf_grade = aclf_grade,
    liver_transplant_listed = listed_transplant,
    icu_admission = icu_admit,
    liver_transplant = transplant_lt_status,
    peak_creatinine = peakhospit_scr,
    AKI_responders = hrs_responders,
    death_in_90days_status = time_to_death_status, # checked 1129
    los = days_to_discharge,
    intubated = mv_use, # checked 1129
    discharge_disposition = disposition,
    creatinine_admission = scr_admit,
    time_90days = time_to_death_90days_cmp,
    status_90days = time_to_death_status_90days_cmp,
    MELD_baseline = admit_meld, # checked 1129
    MELD_Na_baseline = admit_meld_na, # checked 1129
    palliative_care = pall_consult # checked 1129
  ) %>%
  mutate(
    # sex_male==1 -> sex==2 (male)
    sex = if_else(sex == 1, 1, 2), # updated 1129

    # race / ethnicity
    White = if_else(White == 1, 1, 0),
    hispanic_race = if_else(hispanic_race == 1, 1, 0),

    # medication use
    Loop_diuretic = if_else(loop_diuretic == 1, 1, 0),
    aldosterone_antagonist = if_else(aldosterone_antagonist == 1, 1, 0),
    lactulose = if_else(lactulose == 1, 1, 0),
    rifaximin = if_else(rifaximin == 1, 1, 0),
    prophylactic_antibiotic = if_else(prophylactic_antibiotic == 0, 0, 1),
    nsaids = if_else(nsaids == 1, 1, 0),
    beta_blockers = if_else(beta_blockers == 1, 1, 0),
    # rrt
    rrt = ifelse(rrt == 2, 0, rrt),

    # comorbidities
    diabetes = if_else(diabetes == 1, 1, 0),
    cad = if_else(cad == 1, 1, 0),
    htn = if_else(htn == 1, 1, 0),

    # cirrhosis etiology mapping (reverse of your previous)
    etiology_cirrhosis = case_when(
      etiology_cirrhosis == 1 ~ 1,
      etiology_cirrhosis == 3 ~ 2,
      etiology_cirrhosis == 2 ~ 3,
      etiology_cirrhosis %in% c(4, 5) ~ 4,
      etiology_cirrhosis == 6 ~ 5,
      TRUE ~ NA_real_
    ),  # changed 1129

    # complications
    ascites_admission = if_else(ascites_admission == 1, 1, 0),
    encephalopathy_admission = if_else(encephalopathy_admission == 1, 1, 0),
    gi_bleed_admission = if_else(gi_bleed_admission == 1, 1, 0),
    peritonitis_admission = if_else(peritonitis_admission == 1, 1, 0),
    hcc_admission = if_else(hcc_admission == 1, 1, 0),
    tips_admission = if_else(tips_admission == 1, 1, 0),

    # hepatic encephalopathy grade: new(0-4) -> old(1-5)
    he_grade_admission = case_when(
      he_grade_admission == 0 ~ 1,
      he_grade_admission == 1 ~ 2,
      he_grade_admission == 2 ~ 3,
      he_grade_admission == 3 ~ 4,
      he_grade_admission == 4 ~ 5,
      TRUE ~ NA_real_
    ),
    liver_transplant = ifelse(liver_transplant == 1 | liver_transplant == 2, 1, 0),

    discharge_disposition = case_when(
      discharge_disposition == 5 ~ 1,
      discharge_disposition == 1 ~ 2,
      discharge_disposition == 2 ~ 3,
      discharge_disposition == 3 ~ 3,
      discharge_disposition == 4 ~ 4,
      TRUE ~ NA_real_
    ),
    AKI_responders = case_when(
      AKI_responders == 2 ~ "complete response",
      AKI_responders == 1 ~ "partial response",
      AKI_responders == 0 ~ "no response"
    )
  )

create_first_nonzero_value <- function(data, original_variable, new_variable) {
  # Build the expected column names
  day_vars <- paste0(original_variable, "_day", 1:13)

  # Keep only those that exist in the dataset
  valid_day_vars <- day_vars[day_vars %in% names(data)]

  # Apply logic and keep only subjectid + new_variable
  data %>%
    rowwise() %>%
    mutate(
      !!sym(new_variable) := {
        values <- c_across(all_of(valid_day_vars))
        first_valid <- values[!is.na(values) & values != 0]
        if (length(first_valid) > 0) first_valid[1] else NA
      }
    ) %>%
    ungroup() %>%
    select(subjectid, all_of(new_variable))  # keep subjectid + new var
}

var1 <- c(
  "group",
  "age_admission", "sex", "White", "hispanic_race", "loop_diuretic",
  "aldosterone_antagonist", "lactulose", "rifaximin", "prophylactic_antibiotic",
  "nsaids", "beta_blockers", "albumin_amount_admission",
  "diabetes", "cad", "htn", "etiology_cirrhosis",
  "ascites_admission", "encephalopathy_admission", "gi_bleed_admission",
  "peritonitis_admission", "hcc_admission", "tips_admission", "na_admit",
  "k_admit", "cl_admit", "co2_admit", "bun_admit", "urine_creatinine", "fena",
  "he_grade_admission", "baseline_creatinine", "CLIF_C_Score", "aclf_grade",
  "liver_transplant_listed", "icu_admission", "liver_transplant",
  "peak_creatinine", "AKI_responders",
  "creatinine_admission",
  "death_in_90days_status", "los", "discharge_disposition",
  "palliative_care", "intubated", "MELD_baseline",
  "MELD_Na_baseline", "time_90days", "status_90days", "subjectid"
)

final_terlipressin <- terlipressin_numeric %>% select(all_of(var1))
final_terlipressin <- final_terlipressin %>%
  mutate(MELD_Na_baseline = ifelse(is.na(MELD_Na_baseline),
                                   median(MELD_Na_baseline, na.rm = TRUE),
                                   MELD_Na_baseline))

order_names <- names(final_terlipressin)
```

## Off-label vasoconstrictor cohort

Site-level supplements (sediment findings, RRT/CRRT, days to peak and last
creatinine) are merged onto the core registry before harmonising variable coding.

```{r}
#| label: prep-hrs

# read hrs
hrs <- read_excel("/Users/to909/Desktop/Andrew/All_edited_new_12142022.xlsx")

# read additional site-level data
site_vars <- c("study_id", "creatinine_last_available", "nephrology_sediment",
               "granular_casts", "sediment_description", "rrt_crrt",
               "days_peak_cre", "days_last_cre", "albumin_amount_prior")

Baylor0913 <- read_excel("/Users/to909/Desktop/Andrew/Baylor0913.xlsx") %>%
  select(all_of(site_vars))

Indiana0913 <- read_excel("/Users/to909/Desktop/Andrew/Indiana0913.xlsx") %>%
  select(all_of(site_vars))

Jacksonville0913 <- read_excel("/Users/to909/Desktop/Andrew/Jacksonville0913.xlsx") %>%
  select(all_of(site_vars))

Kentukey0913 <- read_excel("/Users/to909/Desktop/Andrew/Kentukey0913.xlsx") %>%
  select(all_of(site_vars))

MCW0913 <- read_excel("/Users/to909/Desktop/Andrew/MCW0913.xlsx") %>%
  select(all_of(site_vars))

MGH0913 <- read_excel("/Users/to909/Desktop/Andrew/MGH0913.xlsx") %>%
  select(all_of(site_vars))

Michigan0913 <- read_excel("/Users/to909/Desktop/Andrew/Michigan0913.xlsx") %>%
  mutate(sediment_description = NA, albumin_amount_prior = NA) %>%
  select(all_of(site_vars))

Oschner0913 <- read_excel("/Users/to909/Desktop/Andrew/Oschner0913.xlsx") %>%
  select(all_of(site_vars))

Rochester0913 <- read_excel("/Users/to909/Desktop/Andrew/Rochester0913.xlsx") %>%
  select(all_of(site_vars))

USC0913 <- read_excel("/Users/to909/Desktop/Andrew/USC0913.xlsx") %>%
  mutate(sediment_description = NA, creatinine_last_available = NA,
         rrt_crrt = NA, days_peak_cre = NA, days_last_cre = NA,
         albumin_amount_prior = NA) %>%
  select(all_of(site_vars))

Yale0913 <- read_excel("/Users/to909/Desktop/Andrew/Yale0913.xlsx") %>%
  select(all_of(site_vars))

addtional_vars <- rbind(
  Baylor0913, Indiana0913, Jacksonville0913, Kentukey0913, MCW0913,
  MGH0913, Michigan0913, Oschner0913, Rochester0913, USC0913, Yale0913
) %>%
  select(-albumin_amount_prior)

# merge all
hrs <- merge(hrs, addtional_vars, by = "study_id", all.x = TRUE) %>%
  rename(subjectid = study_id)

# Clean variables
hrs <- hrs %>%
  mutate(
    White = ifelse(White == 1, 1, 0),
    etiology_cirrhosis = case_when(
      etiology_cirrhosis == 1 ~ 1,
      etiology_cirrhosis == 2 ~ 2,
      etiology_cirrhosis == 3 ~ 3,
      etiology_cirrhosis == 5 ~ 4,
      etiology_cirrhosis %in% c(4, 6, 7) ~ 5,
      TRUE ~ NA_real_
    )
  )

# hrs <- hrs %>%
#   mutate(
#     liver_transplant_90days_time = ifelse(!is.na(days_liver), days_liver, 90),
#     liver_transplant_90days_status=ifelse(!is.na(days_liver),1,0),
#     # Time variable: whichever event happens first
#  # 1. TIME: The time is the minimum of the two event times
#     time_to_death_90days_cmp = pmin(death_in_90days_time, liver_transplant_90days_time, na.rm = TRUE),
#
#     # 2. STATUS: Determine which event happened first
#     status_90days = case_when(
#       # Condition 1: Death happened first (or on the exact same day as transplant)
#       time_to_death_90days_cmp == death_in_90days_time & death_in_90days_status == 1 ~ 1,
#
#       # Condition 2: Transplant happened first before death
#       time_to_death_90days_cmp == liver_transplant_90days_time & liver_transplant_90days_status == 1 ~ 2,
#
#       # Condition 0: Censored (Neither happened by the time of their follow-up/90 days)
#       TRUE ~ 0
#     )
#   )

final_hrs_aki <- hrs %>%
  mutate(group = "hrs") %>%
  filter(final_type_of_aki == 2, hrs_vasoconstrictor == 1) %>%
  select(all_of(order_names)) %>%
  mutate(MELD_Na_baseline = ifelse(is.na(MELD_Na_baseline),
                                   median(MELD_Na_baseline, na.rm = TRUE),
                                   MELD_Na_baseline))
```

## Combined analytic dataset

```{r}
#| label: prep-combined

all_final <- rbind(final_hrs_aki, final_terlipressin) %>%
  mutate(
    liver_transplant = ifelse(is.na(liver_transplant), 0, liver_transplant),
    disposition_new = case_when(
      discharge_disposition == 2 ~ 0,
      discharge_disposition == 3 ~ 1
    ),
    hrs_responders_cat_2 = ifelse(AKI_responders == "no response", 0, 1),
    etiology_cirrhosis_cat2 = ifelse(etiology_cirrhosis == 1, 1, 0),
    group_numerical = ifelse(group == "hrs", 0, 1)
  )

num_var <- c(
  "age_admission",
  "age",
  "albumin_amount_admission",
  "albumintotal_terli_day1", "albumintotal_terli_day2", "albumintotal_terli_day3",
  "albumintotal_terli_day4", "albumintotal_terli_day5", "albumintotal_terli_day6",
  "albumintotal_terli_day7", "albumintotal_terli_day8", "albumintotal_terli_day9",
  "albumintotal_terli_day10", "albumintotal_terli_day11", "albumintotal_terli_day12",
  "albumintotal_terli_day13",
  "totalalbumin_before_terli",
  "na_admit", "sodium_admit", "k_admit", "k_terli_day0", "cl_admit",
  "chloride_terli_day0", "co2_admit", "bicarb_terli_day0", "bun_admit",
  "bun_terli_day0", "creatinine_admission", "scr_admit", "urine_creatinine",
  "ua_cr_value_hrs", "peak_creatinine", "scr_aki", "alt_admit", "alt_terli_day0",
  "tb_admit", "bili_terli_day0", "alb_admit", "albumin_admit", "inr_admit",
  "wbc_admit", "wbc_terli_day0", "plt_admit", "plt_terli_day0", "urine_sodium",
  "ua_na_value_hrs", "fena", "fena_hrs",
  "sbp_admission", "aki_sbp", "dbp_admission", "aki_dbp",
  "MELD_baseline", "admit_meld", "MELD_Na_baseline", "admit_meld_na",
  "clif_score", "MAP", "map_terli_day0_time0", "CLIF_C_Score",
  "baseline_creatinine", "baseline_scr", "los", "days_to_discharge",
  "death_in_90days_time", "dc_days_to_death", "creatinine_admission",
  "time_90days", "site"
)

all_var <- setdiff(names(all_final), "subjectid")
cat_var <- setdiff(all_var, num_var)
```

```{r}
#| label: cohort-counts
#| echo: false

all_final %>%
  count(group) %>%
  mutate(Cohort = ifelse(group == "hrs", "Off-label vasoconstrictor", "Terlipressin")) %>%
  select(Cohort, `Patients (N)` = n) %>%
  gt() %>%
  tab_header(title = "Unmatched analytic cohorts") %>%
  tab_options(table.width = pct(55), heading.title.font.weight = "bold")
```

# Baseline characteristics {#sec-baseline}

## Full baseline comparison by cohort

Continuous variables are summarised as median [IQR] and compared with non-parametric
tests; categorical variables are compared with chi-square tests.

```{r}
#| label: table-one

# create Table 1 for exposure response
T1_all_final_subgroup <- CreateTableOne(
  vars = all_var,
  strata = "group",
  includeNA = FALSE,
  addOverall = TRUE,
  data = all_final,
  factorVars = cat_var
)

T1_all_final_subgroup_csv <- print(
  T1_all_final_subgroup,
  nonnormal = num_var,
  showAllLevels = FALSE,
  missing = TRUE,
  quote = FALSE,
  noSpaces = TRUE,
  printToggle = FALSE
)

write.csv(
  T1_all_final_subgroup_csv,
  file = "/Users/to909/Desktop/Terlipressin projects/Shelsea/Table1_all_final_11302025.csv"
)

T1_all_final_subgroup_csv %>%
  as.data.frame() %>%
  tibble::rownames_to_column("Variable") %>%
  rename(`Off-label vasoconstrictor` = hrs, Terlipressin = terli) %>%
  kable(align = c("l", rep("r", 5)),
        caption = "Table 1. Baseline characteristics, unmatched cohorts") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE, fixed_thead = TRUE) %>%
  scroll_box(height = "520px")
```

## Key baseline variables

```{r}
#| label: table-key-baseline

vars_req1 <- c(
  "etiology_cirrhosis_cat2",
  "baseline_creatinine",
  "albumin_amount_admission",
  "creatinine_admission"
)

T_req1 <- CreateTableOne(
  vars = vars_req1,
  strata = "group",
  includeNA = FALSE,
  addOverall = FALSE,
  data = all_final,
  factorVars = c("etiology_cirrhosis_cat2")
)

T_req1_print <- print(
  T_req1,
  nonnormal = c("baseline_creatinine", "albumin_amount_admission", "creatinine_admission"),
  showAllLevels = FALSE,
  missing = FALSE,
  quote = FALSE,
  noSpaces = TRUE,
  printToggle = FALSE
)

T_req1_print %>%
  as.data.frame() %>%
  tibble::rownames_to_column("Variable") %>%
  rename(`Off-label vasoconstrictor` = hrs, Terlipressin = terli) %>%
  kable(align = c("l", rep("r", 4)),
        caption = "Alcohol-related etiology, baseline and admission creatinine, and albumin (unmatched cohorts)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE)
```

# Propensity-score matching {#sec-matching}

## Matching specification

1:1 nearest-neighbour matching on the logit of a propensity score estimated from
age, sex, ascites at admission, alcohol-related cirrhosis, and baseline MELD-Na,
with a 0.2 SD caliper. Unmatched patients are dropped.

```{r}
#| label: matching

matched_data <- matchit(
  group_numerical ~ age_admission + sex + ascites_admission +
    etiology_cirrhosis_cat2 + MELD_Na_baseline,
  data   = all_final,
  method = "nearest",
  distance = "glm",
  ratio  = 1,
  caliper = 0.2  # common recommendation: 0.2 on PS logit SD
)

matched_data <- match.data(matched_data, drop.unmatched = TRUE)

matched_data %>%
  count(group) %>%
  mutate(Cohort = ifelse(group == "hrs", "Off-label vasoconstrictor", "Terlipressin")) %>%
  select(Cohort, `Matched patients (N)` = n) %>%
  gt() %>%
  tab_header(title = "Matched analytic cohorts") %>%
  tab_options(table.width = pct(55), heading.title.font.weight = "bold")
```

## Covariate balance before matching

```{r}
#| label: balance-before
#| echo: false

bal.tab(
  group_numerical ~ age_admission + sex + ascites_admission +
    etiology_cirrhosis_cat2 + MELD_Na_baseline,
  data    = all_final,
  disp    = c("means", "sds")
)
```

## Covariate balance after matching

```{r}
#| label: balance-after
#| echo: false

bal.tab(
  group_numerical ~ age_admission + sex + ascites_admission +
    etiology_cirrhosis_cat2 + MELD_Na_baseline,
  data    = matched_data,
  treat   = matched_data$group_numerical,
  weights = matched_data$weight.ATE,
  disp    = c("means", "sds")
)
```

# HRS-AKI treatment response {#sec-scr-response}

Everything in this section uses the **matched** cohorts. In the creatinine tables,
`N` is the number of matched patients in each band; response percentages are
calculated among patients with a documented response outcome.

```{r}
#| label: scr-categories

# Serum creatinine at treatment initiation: terlipressin day-0 SCr where available,
# otherwise admission SCr (used for the off-label cohort).
scr_day0 <- terlipressin_numeric %>%
  select(subjectid, scr_terli_day0)

matched_data <- matched_data %>%
  merge(scr_day0, by = "subjectid", all.x = TRUE) %>%
  mutate(scr_terli_day0 = ifelse(is.na(scr_terli_day0), creatinine_admission, scr_terli_day0)) %>%
  rename(scr = scr_terli_day0)

# Creatinine bands. Values below 1.51 mg/dL now get their own explicit level
# instead of being silently dropped into NA.
scr_breaks <- c(-Inf, 1.51, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, Inf)
scr_labels <- c("<1.51", "1.51–1.99", "2.0–2.49", "2.5–2.99", "3.0–3.49",
                "3.5–3.99", "4.0–4.49", "4.5–4.99", "≥5.0")

matched_data <- matched_data %>%
  mutate(
    scr_cat             = cut(scr, breaks = scr_breaks, labels = scr_labels, right = FALSE),
    peak_creatinine_cat = cut(peak_creatinine, breaks = scr_breaks, labels = scr_labels, right = FALSE)
  ) %>%
  mutate(across(c(scr_cat, peak_creatinine_cat),
                ~ forcats::fct_na_value_to_level(.x, "Missing")))

# Responders by creatinine band, with N for each cohort and overall.
resp_by_cat <- function(data, catvar) {
  cat_sym <- rlang::sym(catvar)

  by_grp <- data %>%
    group_by(!!cat_sym, group) %>%
    summarise(N      = n(),
              n_resp = sum(hrs_responders_cat_2 == 1, na.rm = TRUE),
              n_eval = sum(!is.na(hrs_responders_cat_2)),
              .groups = "drop") %>%
    tidyr::pivot_wider(id_cols = !!cat_sym, names_from = group,
                       values_from = c(N, n_resp, n_eval), values_fill = 0)

  overall <- data %>%
    group_by(!!cat_sym) %>%
    summarise(N_all      = n(),
              n_resp_all = sum(hrs_responders_cat_2 == 1, na.rm = TRUE),
              n_eval_all = sum(!is.na(hrs_responders_cat_2)),
              .groups = "drop")

  by_grp %>%
    left_join(overall, by = catvar) %>%
    arrange(!!cat_sym) %>%
    mutate(
      resp_hrs   = sprintf("%d (%.1f)", n_resp_hrs,   100 * n_resp_hrs   / pmax(n_eval_hrs, 1)),
      resp_terli = sprintf("%d (%.1f)", n_resp_terli, 100 * n_resp_terli / pmax(n_eval_terli, 1)),
      resp_all   = sprintf("%d (%.1f)", n_resp_all,   100 * n_resp_all   / pmax(n_eval_all, 1))
    ) %>%
    select(band = !!cat_sym,
           N_hrs, resp_hrs, N_terli, resp_terli, N_all, resp_all)
}

resp_gt <- function(tab, band_label, title, subtitle) {
  tab %>%
    gt() %>%
    cols_label(band = band_label,
               N_hrs = "N", resp_hrs = "Response, n (%)",
               N_terli = "N", resp_terli = "Response, n (%)",
               N_all = "N", resp_all = "Response, n (%)") %>%
    tab_spanner(label = "Off-label vasoconstrictor", columns = c(N_hrs, resp_hrs)) %>%
    tab_spanner(label = "Terlipressin", columns = c(N_terli, resp_terli)) %>%
    tab_spanner(label = "Overall", columns = c(N_all, resp_all)) %>%
    tab_header(title = title, subtitle = subtitle) %>%
    cols_align(align = "center", columns = -band) %>%
    tab_style(style = cell_text(weight = "bold"),
              locations = list(cells_column_labels(), cells_column_spanners())) %>%
    tab_style(style = cell_fill(color = "#f4f8fb"),
              locations = cells_body(columns = c(N_all, resp_all))) %>%
    tab_footnote(
      footnote = "Response = complete or partial HRS-AKI response (hrs_responders_cat_2 = 1). Percentages use patients with a documented response outcome as the denominator; one off-label patient has a missing response status.",
      locations = cells_column_spanners(spanners = "Overall")
    ) %>%
    tab_options(heading.title.font.weight = "bold",
                table.font.size = pct(95),
                data_row.padding = px(4))
}
```

## Overall response by cohort

```{r}
#| label: tbl-response-overall

matched_data <- matched_data %>%
  mutate(AKI_responders_cat2 = ifelse(AKI_responders == "no response",
                                      "no response", "overall response"))

CreateTableOne(
  vars = "AKI_responders_cat2",
  strata = "group",
  data = matched_data,
  factorVars = "AKI_responders_cat2"
) %>%
  print(printToggle = FALSE) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("Variable") %>%
  rename(`Off-label vasoconstrictor` = hrs, Terlipressin = terli) %>%
  kable(align = c("l", rep("r", 4)),
        caption = "Overall HRS-AKI response by cohort (matched)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = FALSE)
```

## Serum creatinine at treatment initiation vs. response

Day-0 serum creatinine for the terlipressin cohort, admission serum creatinine for
the off-label cohort.

```{r}
#| label: tbl-scr-initiation

tab_req2 <- resp_by_cat(matched_data, "scr_cat")

resp_gt(
  tab_req2,
  band_label = "SCr at initiation (mg/dL)",
  title = "HRS-AKI response by serum creatinine at treatment initiation",
  subtitle = "Matched cohorts"
)
```

## Peak in-hospital serum creatinine vs. response

```{r}
#| label: tbl-scr-peak

tab_req3 <- resp_by_cat(matched_data, "peak_creatinine_cat")

resp_gt(
  tab_req3,
  band_label = "Peak SCr (mg/dL)",
  title = "HRS-AKI response by peak in-hospital serum creatinine",
  subtitle = "Matched cohorts"
)
```

# Ninety-day survival by treatment response {#sec-survival-response}

Patients are split by cohort (`group`) and by HRS-AKI response
(`hrs_responders_cat_2`: response = complete or partial). Kaplan–Meier estimates
treat death as the event and censor liver transplant at the time of transplant; the
competing-risk view in @sec-cuminc-response treats transplant as a competing event.

```{r}
#| label: surv-data

surv_dat <- matched_data %>%
  mutate(status_90days = as.numeric(as.character(status_90days))) %>%
  filter(!is.na(hrs_responders_cat_2)) %>%
  mutate(
    cohort = factor(ifelse(group == "hrs", "Off-label vasoconstrictor", "Terlipressin"),
                    levels = c("Off-label vasoconstrictor", "Terlipressin")),
    response = factor(ifelse(hrs_responders_cat_2 == 1, "Response", "No response"),
                      levels = c("No response", "Response")),
    death      = as.numeric(status_90days == 1),
    transplant = as.numeric(status_90days == 2)
  )
```

## Survival estimates at 90 days

```{r}
#| label: tbl-surv-90d

km_row <- function(d, label_cohort, label_resp) {
  f <- survfit(Surv(time_90days, death) ~ 1, data = d)
  s <- summary(f, times = 90, extend = TRUE)
  tibble(
    Cohort = label_cohort, Response = label_resp,
    N = nrow(d), Deaths = sum(d$death), Transplants = sum(d$transplant),
    surv = 100 * s$surv, lo = 100 * s$lower, hi = 100 * s$upper
  )
}

surv_tab <- bind_rows(
  surv_dat %>% group_split(cohort) %>%
    purrr::map_dfr(~ km_row(.x, as.character(.x$cohort[1]), "All patients")),
  surv_dat %>% group_split(cohort, response) %>%
    purrr::map_dfr(~ km_row(.x, as.character(.x$cohort[1]), as.character(.x$response[1])))
) %>%
  mutate(Response = factor(Response, levels = c("All patients", "No response", "Response"))) %>%
  arrange(Cohort, Response) %>%
  mutate(surv_ci = sprintf("%.1f (%.1f–%.1f)", surv, lo, hi)) %>%
  select(Cohort, Response, N, Deaths, Transplants, surv_ci)

surv_tab %>%
  gt(groupname_col = "Cohort") %>%
  cols_label(Response = "Group", N = "N",
             Deaths = "Deaths by 90 d", Transplants = "Transplants by 90 d",
             surv_ci = "90-day survival, % (95% CI)") %>%
  tab_header(title = "Ninety-day survival by cohort and HRS-AKI response",
             subtitle = "Kaplan–Meier estimates; transplant censored") %>%
  cols_align(align = "center", columns = c(N, Deaths, Transplants, surv_ci)) %>%
  tab_style(style = cell_text(weight = "bold"),
            locations = list(cells_column_labels(), cells_row_groups())) %>%
  tab_style(style = cell_text(style = "italic"),
            locations = cells_body(columns = Response,
                                   rows = Response == "All patients")) %>%
  tab_options(heading.title.font.weight = "bold", data_row.padding = px(4))
```

## Kaplan–Meier curves

```{r}
#| label: fig-km-response
#| fig-cap:
#|   - "Ninety-day survival by HRS-AKI response — off-label vasoconstrictor cohort."
#|   - "Ninety-day survival by HRS-AKI response — terlipressin cohort."
#| fig-width: 6.2
#| fig-height: 5
#| layout-ncol: 2

km_plot <- function(d, title) {
  survfit2(Surv(time_90days, death) ~ response, data = d) %>%
    ggsurvfit(linewidth = 0.9) +
    add_confidence_interval(alpha = 0.12) +
    add_risktable(risktable_stats = "n.risk", size = 3.2) +
    add_risktable_strata_symbol(symbol = "\U25CF", size = 11) +
    add_pvalue(location = "annotation", caption = "Log-rank {p.value}",
               x = 5, y = 0.06, hjust = 0, size = 3.6) +
    scale_x_continuous(breaks = seq(0, 90, 15), limits = c(0, 90),
                       expand = expansion(add = c(3.5, 1.5))) +
    scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
    scale_color_manual(values = c("No response" = col_no_resp, "Response" = col_resp)) +
    scale_fill_manual(values  = c("No response" = col_no_resp, "Response" = col_resp)) +
    labs(title = title, x = "Days from treatment initiation", y = "Survival probability") +
    theme_classic(base_size = 12) +
    theme(legend.position = "top", legend.title = element_blank(),
          plot.title = element_text(face = "bold", size = 12))
}

km_plot(filter(surv_dat, cohort == "Off-label vasoconstrictor"), "Off-label vasoconstrictor")
km_plot(filter(surv_dat, cohort == "Terlipressin"), "Terlipressin")
```

## Association of response with 90-day mortality

Unadjusted Cox models fitted separately within each cohort, with response as the
only covariate.

```{r}
#| label: tbl-cox-response

cox_tab <- purrr::map_dfr(levels(surv_dat$cohort), function(cc) {
  d  <- surv_dat %>% filter(cohort == cc)
  sd <- survdiff(Surv(time_90days, death) ~ response, data = d)
  cx <- summary(coxph(Surv(time_90days, death) ~ response, data = d))
  tibble(
    Cohort = cc,
    hr  = sprintf("%.2f (%.2f–%.2f)", cx$conf.int[1], cx$conf.int[3], cx$conf.int[4]),
    p_cox = cx$coefficients[5],
    p_lr  = pchisq(sd$chisq, df = 1, lower.tail = FALSE)
  )
}) %>%
  mutate(across(c(p_cox, p_lr),
                ~ ifelse(.x < 0.001, "<0.001", sprintf("%.3f", .x))))

cox_tab %>%
  gt() %>%
  cols_label(Cohort = "Cohort",
             hr = "HR for death, response vs. no response (95% CI)",
             p_cox = "Cox p", p_lr = "Log-rank p") %>%
  tab_header(title = "Unadjusted association of HRS-AKI response with 90-day mortality") %>%
  cols_align(align = "center", columns = c(hr, p_cox, p_lr)) %>%
  tab_style(style = cell_text(weight = "bold"), locations = cells_column_labels()) %>%
  tab_options(heading.title.font.weight = "bold", data_row.padding = px(4))
```

## Competing-risk cumulative incidence {#sec-cuminc-response}

Liver transplant is treated as a competing event, so these estimates are the
probability of dying by day 90 accounting for transplant.

```{r}
#| label: tbl-cuminc-response

ci_tab <- purrr::map_dfr(levels(surv_dat$cohort), function(cc) {
  d  <- surv_dat %>% filter(cohort == cc) %>% mutate(st = factor(status_90days))
  ci <- tidycmprsk::cuminc(Surv(time_90days, st) ~ response, data = d)
  ci %>%
    tidy(times = 90) %>%
    filter(outcome == "1") %>%
    transmute(Cohort = cc, Response = as.character(strata),
              est = sprintf("%.1f (%.1f–%.1f)",
                            100 * estimate, 100 * conf.low, 100 * conf.high),
              p_gray = ci$cmprsk$Tests["1", "pv"])
}) %>%
  mutate(p_gray = ifelse(p_gray < 0.001, "<0.001", sprintf("%.3f", p_gray))) %>%
  # Gray's test is a single test per cohort; blank the repeat so it does not read
  # as two independent p-values.
  mutate(p_gray = ifelse(duplicated(Cohort), "", p_gray))

ci_tab %>%
  gt(groupname_col = "Cohort") %>%
  cols_label(Response = "Group",
             est = "90-day cumulative incidence of death, % (95% CI)",
             p_gray = "Gray's test p") %>%
  tab_header(title = "Ninety-day cumulative incidence of death by HRS-AKI response",
             subtitle = "Liver transplant treated as a competing event") %>%
  cols_align(align = "center", columns = c(est, p_gray)) %>%
  tab_style(style = cell_text(weight = "bold"),
            locations = list(cells_column_labels(), cells_row_groups())) %>%
  tab_options(heading.title.font.weight = "bold", data_row.padding = px(4))
```

```{r}
#| label: fig-cuminc-response
#| fig-cap:
#|   - "Cumulative incidence of death by day 90 by HRS-AKI response — off-label vasoconstrictor cohort."
#|   - "Cumulative incidence of death by day 90 by HRS-AKI response — terlipressin cohort."
#| fig-width: 6.2
#| fig-height: 4.6
#| layout-ncol: 2

cuminc_plot <- function(d, title) {
  d <- d %>% mutate(st = factor(status_90days))
  tidycmprsk::cuminc(Surv(time_90days, st) ~ response, data = d) %>%
    ggcuminc(outcome = "1", linewidth = 0.9) +
    add_confidence_interval(alpha = 0.12) +
    scale_x_continuous(breaks = seq(0, 90, 15), limits = c(0, 90),
                       expand = expansion(add = c(1, 1.5))) +
    scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
    scale_color_manual(values = c("No response" = col_no_resp, "Response" = col_resp)) +
    scale_fill_manual(values  = c("No response" = col_no_resp, "Response" = col_resp)) +
    labs(title = title, x = "Days from treatment initiation",
         y = "Cumulative incidence of death") +
    theme_classic(base_size = 12) +
    theme(legend.position = "top", legend.title = element_blank(),
          plot.title = element_text(face = "bold", size = 12))
}

cuminc_plot(filter(surv_dat, cohort == "Off-label vasoconstrictor"), "Off-label vasoconstrictor")
cuminc_plot(filter(surv_dat, cohort == "Terlipressin"), "Terlipressin")
```

# Ninety-day mortality: cohort comparison {#sec-cohort-mortality}

## Cumulative incidence of death by cohort

```{r}
#| label: fig-cuminc-cohort
#| fig-cap: "Cumulative incidence of death by day 90, terlipressin vs. off-label vasoconstrictors (matched cohorts, transplant as competing event)."
#| fig-width: 7.5
#| fig-height: 5

matched_data$status_90days <- as.factor(matched_data$status_90days)

ci_obj <- tidycmprsk::cuminc(
  formula = Surv(time_90days, status_90days) ~ group,
  data = matched_data,
  cencode = 0
)

ggsurvfit::ggcuminc(ci_obj, linewidth = 0.9) +
  add_confidence_interval(alpha = 0.12) +
  # No `color =` title here: naming only the colour guide splits it from the
  # confidence-interval fill guide and draws the legend twice.
  labs(x = "Days from treatment initiation",
       y = "Cumulative incidence of death") +
  scale_x_continuous(breaks = seq(0, 90, by = 15), limits = c(0, 90),
                     expand = expansion(add = c(1, 1.5))) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  scale_color_manual(values = c("hrs" = col_hrs, "terli" = col_terli),
                     labels = c("Off-label vasoconstrictor", "Terlipressin")) +
  scale_fill_manual(values = c("hrs" = col_hrs, "terli" = col_terli),
                    labels = c("Off-label vasoconstrictor", "Terlipressin")) +
  theme_classic(base_size = 12) +
  theme(legend.position = "top", legend.title = element_blank())
```

## Fine–Gray models

Subdistribution hazard of death within 90 days, with liver transplant as the
competing event.

### Unadjusted

```{r}
#| label: fg-crude

matched_data$status_90days <- as.factor(matched_data$status_90days)
tidycmprsk::crr(Surv(time_90days, status_90days) ~ group,
                failcode = 1, cencode = 0, data = matched_data) %>%
  tbl_regression(exp = TRUE) %>%
  add_n() %>%
  bold_p(0.05) %>%   # bold p-values under a given threshold (default 0.05)
  bold_labels()      # bold variable labels with significant p-values
```

### Adjusted for CLIF-C score

```{r}
#| label: fg-clif

tidycmprsk::crr(Surv(time_90days, status_90days) ~ group + CLIF_C_Score,
                failcode = 1, cencode = 0, data = matched_data) %>%
  tbl_regression(exp = TRUE) %>%
  add_n()
```

### Fully adjusted

```{r}
#| label: fg-full

tidycmprsk::crr(
  Surv(time_90days, status_90days) ~ group + CLIF_C_Score +
    prophylactic_antibiotic + beta_blockers + k_admit + cl_admit,
  failcode = 1, cencode = 0, data = matched_data
) %>%
  tbl_regression(exp = TRUE) %>%
  add_n()
```

### Adjusted for CLIF-C, age, GI bleed, and albumin

```{r}
#| label: fg-clinical-death

tidycmprsk::crr(
  Surv(time_90days, status_90days) ~ group + CLIF_C_Score + age_admission +
    gi_bleed_admission + albumin_amount_admission,
  failcode = 1, cencode = 0, data = matched_data
) %>%
  tbl_regression(exp = TRUE) %>%
  add_n() %>%
  bold_p(0.05) %>%
  bold_labels()
```

### Liver transplant as the outcome

Same covariates, but modelling the subdistribution hazard of **liver transplant**
(`failcode = 2`), with death as the competing event.

```{r}
#| label: fg-clinical-transplant

tidycmprsk::crr(
  Surv(time_90days, status_90days) ~ group + CLIF_C_Score + age_admission +
    gi_bleed_admission + albumin_amount_admission,
  failcode = 2, cencode = 0, data = matched_data
) %>%
  tbl_regression(exp = TRUE) %>%
  add_n() %>%
  bold_p(0.05) %>%
  bold_labels()
```

# Supportive care and cohort composition {#sec-sites}

## Renal replacement therapy by cohort

`rrt` for the terlipressin cohort and `rrt_crrt` for the off-label cohort are
combined into a single indicator before tabulating.

```{r}
#| label: tbl-rrt

# Build unified rrt variable from both cohorts
rrt_terli <- terlipressin_numeric %>%
  select(subjectid, rrt) %>%
  mutate(rrt = as.numeric(rrt))

rrt_hrs <- hrs %>%
  select(subjectid, rrt_crrt) %>%
  rename(rrt = rrt_crrt) %>%
  mutate(rrt = as.numeric(rrt))

rrt_all <- bind_rows(rrt_terli, rrt_hrs) %>%
  distinct(subjectid, .keep_all = TRUE)

matched_data_rrt <- matched_data %>%
  left_join(rrt_all, by = "subjectid")

CreateTableOne(
  vars = "rrt",
  strata = "group",
  data = matched_data_rrt,
  factorVars = "rrt"
) %>%
  # `rrt_crrt` is unrecorded for much of the off-label cohort, so show the
  # missing count: tableone's percentages use non-missing denominators.
  print(printToggle = FALSE, missing = TRUE) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("Variable") %>%
  rename(`Off-label vasoconstrictor` = hrs, Terlipressin = terli) %>%
  kable(align = c("l", rep("r", 5)),
        caption = "Renal replacement therapy by cohort (matched)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = FALSE)
```

## Terlipressin patients by site

Site is taken from the prefix of `subjectid`.

```{r}
#| label: tbl-sites-terli

terli_matched <- matched_data %>%
  filter(group == "terli") %>%
  mutate(site = gsub("-.*", "", subjectid))

terli_matched %>%
  count(site, name = "Patients") %>%
  arrange(desc(Patients)) %>%
  rename(Site = site) %>%
  gt() %>%
  tab_header(title = "Matched terlipressin patients by site") %>%
  cols_align(align = "center", columns = Patients) %>%
  tab_style(style = cell_text(weight = "bold"), locations = cells_column_labels()) %>%
  tab_options(table.width = pct(55), heading.title.font.weight = "bold",
              data_row.padding = px(4))
```

## Total albumin by respiratory failure (terlipressin cohort)

```{r}
#| label: tbl-albumin-respfail

CreateTableOne(
  vars = "total_albumin",
  strata = "terli_ae_respfail",
  data = terlipressin_numeric,
  factorVars = NULL
) %>%
  print(nonnormal = "total_albumin", printToggle = FALSE) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("Variable") %>%
  kable(align = c("l", rep("r", 4)),
        caption = "Total albumin by terlipressin-associated respiratory failure") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = FALSE)
```
